Data Preparation

### 2019-01-10 Data Preparation.Rmd
simplify code for d_transcript

```{r}
d_transcript <- d_transcript %>%
  select(`Student Number`, `Module (Abbrev.)`, `Module (Desc.)`,
         `Program (Description)`, `Academic Year`, `Academic Session`,
         `Appraisal (Description)`,
         `Number rep. attemp`, `Grade symbol`, `Booking Status (Desc.)`) %>%
  rename(`Student ID Number` = `Student Number`,
         `Course Code` = `Module (Abbrev.)`,
         `Course Title` = `Module (Desc.)`,
         `Study Program` = `Program (Description)`,
         `Civil Year` = `Academic Year`, # double check
         `Period` = `Academic Session`,
         `Appraisal` = `Appraisal (Description)`, # is there a better name for the variable?
         `Number Repeated Attempt` = `Number rep. attemp`,
         `Grade` = `Grade symbol`,
         `Status` = `Booking Status (Desc.)`) # is there a better name for the variable?
```

@@

```{r}
d_reduce <- d_rename %>%
  select(-not_keep,-Session,-`Program Abbreviation`)

d_reduce <- d_reduce[!duplicated(d_reduce),]
```
###Extracting grades
We notice that there are several values under `Grade` for the same course. We are interested in keeping only the final grades, corresponding to the rows where `Appraisal Title` is marked as "Grade supervisor". 
So lets extract the grades and add the course concentration by keeping the first three letters of the `Code`:

```{r}
d_grade <- d_reduce %>%
  filter(`Appraisal Title` == "Grade supervisor") %>%
  mutate(`Course concentration` = substr(Code, start = 1, stop = 3))

d_grade <- d_grade[!duplicated(d_grade),]
```

>>>>

```{r}
d_transcript <- d_transcript %>%
  filter(`Appraisal (Description)` == "Grade supervisor")
  select(`Student Number`, `Module (Abbrev.)`, `Module (Desc.)`,
         `Program (Description)`, `Academic Year`, `Academic Session`,
         `Number rep. attemp`, `Grade symbol`, `Booking Status (Desc.)`) %>%
  distinct %>%
  rename(`Student ID Number` = `Student Number`,
         `Course Code` = `Module (Abbrev.)`,
         `Course Title` = `Module (Desc.)`,
         `Study Program` = `Program (Description)`,
         `Civil Year` = `Academic Year`, # double check
         `Period` = `Academic Session`,
         `Number Repeated Attempt` = `Number rep. attemp`,
         `Grade` = `Grade symbol`,
         `Status` = `Booking Status (Desc.)`) # is there a better name for the variable?
```

@@

```
###Extracting grades
We notice that there are several values under `Grade` for the same course. We are interested in keeping only the final grades, corresponding to the rows where `Appraisal Title` is marked as "Grade supervisor". 
So lets extract the grades and add the course concentration by keeping the first three letters of the `Code`:
